\section{Workshop}

One workshop was organized to refine the concept of coupling criteria.

\subsection{\formatdate{19}{10}{2015} at Z\"uhlke}

\textbf{Agenda}

\begin{enumerate}
\item Introduction
\item Brainstorming Coupling Criteria
\item Refinement of prepared Coupling catalog.
\end{enumerate}

\textbf{Attendees:} Wolfgang Giersche, Olaf Zimmermann (ZIO), Lukas Kölbener (KOE), Michael Gysel (GYS)

\textbf{Notes}

CC Cards Layout:

\begin{itemize}
\item Identity \& Lifecycle
\item Business Transactions | Volatility | Resilience
\item Security Constraints | Consistency
\item Network Traffic | Storage
\item Predefined Services | Change Management
\end{itemize}


\textbf{Decisions}

\begin{itemize}
\item 10 Coupling Criteria will be finally approved in the next meeting.
\item \enquote{Identity \& Lifecycle}, \enquote{Business Transaction}, \enquote{Volatility} and \enquote{Resilience} are the most important CC to be implemented first.
\end{itemize}

\textbf{Action Items}

\begin{itemize}
\item GYS/KOE: Finalize Coupling Criteria catalog. (22.10.2015)
\item ZIO: Provide slides about master data categorization (information integration?). (22.10.2015)
\item Giersche: Provide model (and maybe a contact) of an internal software project. (22.10.2015)
\item GYS/KOE: Prepare quantification concept for coupling criteria. (22.10.2015)
\item GYS/KOE: Add aggregation types, n-n relations and inheritance to example model. (23.10.2015)
\item ZIO: Send pictures of CC cards. (22.10.2015)
\end{itemize}